The growth of children's semantic and phonological networks: insight from 10 languages

### 2020-04-03 journal/ms.tex
final revisins

Correspondence concerning this article should be addressed to Abdellah Fourtassi, Postal address. E-mail: afourtas@stanford.edu}
\keywords{Word learning; semantic network; phonological network; network growth; cross-linguistic analysis.}
\usepackage{lineno}

@@

\#Introduction

@@

Since the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across 10 languages. Semantic associations are not necessarily shared across languages, but we use this technique as a reasonable first approximation. In support of this approximation, Youn et al. (2016) showed that semantic networks across languages share substantial similarities. The fact that semantic associations are assumed to be shared across languages does not mean that the semantic networks will necessarily grow in a similar fashion. For instance, the set of words acquired by children as well as the order of word acquisition can vary from language to language leading to possibily different learning strategies.

@@

In previous studies, two nodes were linked if they had an edit distance of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009). However, these studies reported a contribution of phonological connectivity to noun learning when networks were built using a dense adult vocabulary. Since the focus of the current study is on the mechanism of growth, the networks are based on children's early vocabulary. The latter, however, contains very few noun pairs with an edit distance of 1. To better represent the similarity space in the phonological domain, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1. We also show the results for phonological networks where the edges between pairs of words were weighted by the inverse of the edit distance. We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").} The connectivity of a given node was characterized with its \emph{degree}: the number of links it shares with other words.

@@

\#\#\#Connectivity predicts the age of acquisition

@@

\#\#\#Power-law degree distribution

@@

\caption{\label{tab:powerLawProd}Results of fitting a power law model to the degree (i.e., connectivity) distribution in each model for production data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
\midrule
Croatian & 4 & 2.55 & 0.881 & 4 & 2.18 & 0.123\\
Danish & 4 & 2.38 & 0.001 & 11 & 4.55 & 0.858\\
English & 5 & 2.66 & 0.132 & 20 & 9.14 & 0.511\\
French & 8 & 2.81 & 0.133 & 20 & 3.75 & 0.112\\
Italian & 4 & 2.93 & 0.608 & 9 & 9.45 & 0.780\\
Norwegian & 5 & 2.88 & 0.201 & 15 & 6.28 & 0.744\\
Russian & 24 & 5.61 & 0.723 & 8 & 4.20 & 0.541\\
Spanish & 4 & 2.98 & 0.460 & 13 & 8.75 & 0.736\\
Swedish & 4 & 2.49 & 0.171 & 11 & 4.68 & 0.103\\
Turkish & 4 & 2.87 & 0.925 & 8 & 3.26 & 0.375\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:powerLawComp}Results of fitting a power law model to the degree distribution in each model for comprehension data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
\midrule
Croatian & 5 & 2.67 & 0.895 & 2 & 2.06 & 0.020\\
Danish & 4 & 2.39 & 0.005 & 5 & 2.98 & 0.136\\
English & 4 & 2.64 & 0.765 & 13 & 5.16 & 0.235\\
French & 4 & 2.63 & 0.330 & 18 & 5.58 & 0.336\\
Italian & 4 & 2.88 & 0.688 & 8 & 10.27 & 0.909\\
Norwegian & 5 & 2.87 & 0.433 & 13 & 7.65 & 0.440\\
Russian & 8 & 3.91 & 0.952 & 5 & 3.97 & 0.854\\
Spanish & 5 & 3.11 & 0.552 & 5 & 3.01 & 0.085\\
Swedish & 5 & 2.81 & 0.713 & 9 & 6.75 & 0.102\\
Turkish & 4 & 3.13 & 0.887 & 9 & 5.73 & 0.958\\
\bottomrule
\end{tabular}
\end{table}

In brief, the analysis consisted in two steps. First, we derived the optimal cut-off, \(k_{min}\), above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter \(\alpha\). Second, we calculated the goodness-to-fit, which resulted in a \(p\)-value quantifying the plausibility of the model. The results are shown in Table \ref{tab:powerLawProd} for production data, and in Table \ref{tab:powerLawComp} for comprehension data.

Overall, we could not reject the null hypothesis of a power-law distribution: The \(p\)-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. These \enquote{truncated} power-laws in phonological networks may be due to the constraints that exist on word formation in the phonological domain such as the size of the phonemic inventory, phonotactic rules, and word length. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law (Arbesman et al., 2010).

@@

We estimated the parameter \(\beta\) using a Bayesian approach. The inference was performed using the probabilistic programming language WebPPL (Goodman \& Stuhlmuller, 2014). We defined a uniform prior over \(\beta\), and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using Formula 1). Markov Chain Monte Carlo sampling resulted in a posterior distribution over \(\beta\), which we summarized in Figure \ref{fig:growthPred}. The results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT. Crucially, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages. This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption; rather, it supports our initial approximation about the shared nature of the semantic similarity measure. That said, this approximation is not perfect. For example, there is evidence that a small part of the variance in free association data can be explained by phonological similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson, 2018), thus leading to possibly minor cross-linguistic differences.} and phonological domains.

@@

As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences. Connectivity contributes to learning in some languages but not in other. In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This finding contrasts with the original finding in Hills et al. (2009). However, this difference might be due to our using a slightly different model (which included word length as a covariate) and a larger dataset. That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model (Figure \ref{fig:staticAll}).

@@

One possibility is that these patterns emerge from children's use of statistical learning abilities (Aslin \& Newport, 2012; Saffran, Aslin, \& Newport, 1996; Smith \& Yu, 2008). The term \enquote{statistical learning} has been used in the developmental literature to describes the process by which one acquires information about their environment through tracking the frequency distribution of some elements (e.g., words) in different contexts. An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input. Previous work in this line of research has documented specific mechanisms which can explain the patterns found in the current study.

For example, in the semantic domain, growth according to EXT could be explained by a mechanism similar to cross-situational learning (McMurray et al., 2012; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents. The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word \enquote{ball} is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings. In our case, free association (used to determine semantic network connectivity) is related to contextual co-occurrence (Fourtassi \& Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected words will tend to occur in a variety of speech and referential contexts. This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts. Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur (hence the similarity with EXT). This possibility is supported by the finding that words' diversity of occurrence in child-directed speech predicts their age of learning (Hills et al., 2010; Stella et al., 2017).

@@

This work shares a number of limitations with previous studies using similar research strategy and datasets. Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional). Such a measure has been shown to be valid and reliable (Fenson et al., 1994), and has allowed researchers to study important aspects of word learning (Braginsky et al., 2019; Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel, 2009). In our case, the use of cost-effective cross-sectional data has allowed us to leverage large-scale studies across several languages. That said, it is important to remember that this type of data can only inform us about the learning trajectory of the \enquote{average} child. Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage \& Colunga, n.d.). To illustrate, some children develop \enquote{islands of expertise,} that is, well-organized knowledge about a certain topic (e.g., birds or dinosaurs). This prior knowledge enables these children to learn new related words more easily (e.g., Chi \& Koeske, 1983).

@@

\hypertarget{appendix-a-analyses-using-different-phnonological-distances}{%
\section{Appendix A: Analyses using different phnonological distances}\label{appendix-a-analyses-using-different-phnonological-distances}}

@@

We show in Figure \ref{fig:corrPlot} the correlation between the phonological connectivity and age of acquisition in both comprehension and production. The sparsity issue --- due to the low phonological neighborhood in the children's lexicon --- is apparent: Most words had 0 connectivity, and a few had non-zero but small degrees. The values of the correlations are much lower than the ones obtained with the threshold of 2.

The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comaprison to semEXT and other predictors of learning in each language (Figure \ref{fig:staticPredEdit1} and across all languages (Figure \ref{fig:staticAllEdit}). These figures show that phonoEXT based on edit distance 1 had no noticeable effect on learning.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in the phonological networks, using an edit distance of 1. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPredEdit1-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression models. The phonologocal networks were based on an edit distance of 1. Ranges indicate 95\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).}\label{fig:staticPredEdit1}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model. The phonologocal networks were based on an edit distance of 1. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllEdit}
\end{figure}

@@

We constructed weighted phonological networks where the edge between a given pair of words \((w_1, w_2)\) was wieghted by \(\frac{1}{edit(w_1,w_2)}\). The phonological connectivity of a given word \(w\) was defined as the sum over all weighted edges with every other word \(w_i\) in the network, i.e., \(\sum_{i} \frac{1}{edit(w,w_i)}\).

The results were as follows. On the one hand, the correlations were generally high and in many cases (especially in the production data), higher than the ones obtained with the thresholds 2 and 1 (Figure \ref{fig:corrPlotnt}). On the other hand, phonoEXT resulted in very noisy estimates when we controlled for frequency and length (Figures \ref{fig:staticPrednt} and \ref{fig:staticAllnt}). The reason was that the new phonological connectivity was very highly correlated with length. The average correlation across languages was \(r =\) -0.95 for production data (compared to -0.29 and -0.60 for the phonological networks with an edit distance of 1 and 2, respectvely). This fact lead to a collinearity issue in the regression, making the effects hard to estimate and interpret.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlotnt-1} \caption{Age of acquistion in both comprehension and production as predicted by the connectivity in the phonological network, using weighted edges. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlotnt}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPrednt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression models. In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance. Ranges indicate 95\% confidence intervals. Positive values indicate a positive relationship (e.g., longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g., words with higher frequency tend to have a lower AoA).}\label{fig:staticPrednt}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model. In the phonological networks, the edges between pairs of words were weighted by the inverse of the edit distance. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllnt}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPair-1} \caption{The distribution of the Pearson correlation coefficents of the unilemma's phonological connectivity between every pair of languages.}\label{fig:corrPair}
\end{figure}

@@

\leavevmode\hypertarget{ref-beckage}{}%
Beckage, N. M., \& Colunga, E. (n.d.). Network growth modeling to capture individual lexical learning.

@@

>>>>

Correspondence concerning this article should be addressed to Abdellah Fourtassi, Postal address. E-mail: abdellah.fourtassi@gmail.com}
\keywords{Word learning; semantic network; phonological network; network growth; cross-linguistic analysis.}
\usepackage{lineno}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

Since the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across 10 languages. Semantic associations are not necessarily shared across languages, but we use this technique as a reasonable first approximation. In support of this approximation, Youn et al. (2016) showed that semantic networks across languages share substantial similarities. The fact that semantic associations are assumed to be shared across languages does not mean that the semantic networks will necessarily grow in a similar fashion. For instance, the set of words acquired by children as well as the order of word acquisition can vary from language to language leading to possibly different learning strategies.

@@

In previous studies, two nodes were linked if they had an edit distance of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009). However, these studies reported a contribution of phonological connectivity to noun learning when networks were built using a dense adult vocabulary. Since the focus of the current study is on the mechanism of growth, the networks are based on children's early vocabulary. The latter, however, contains very few noun pairs with an edit distance of 1. To better represent the similarity space in the phonological domain, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1. We also show the results for phonological networks where the edges between pairs of words were weighted by a normalized edit distance. We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").} The connectivity of a given node was characterized with its \emph{degree}: the number of links it shares with other words.

@@

\hypertarget{connectivity-predicts-the-age-of-acquisition}{%
\subsubsection{Connectivity predicts the age of acquisition}\label{connectivity-predicts-the-age-of-acquisition}}

@@

\hypertarget{power-law-degree-distribution}{%
\subsubsection{Power-law degree distribution}\label{power-law-degree-distribution}}

@@

\caption{\label{tab:powerLawProd}Results of fitting a power-law model to the degree (i.e., connectivity) distribution in each model for production data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power-law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Sem.} & \multicolumn{3}{c}{Phono.} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
\midrule
Croatian & 4 & 2.55 & 0.881 & 4 & 2.18 & 0.123\\
Danish & 4 & 2.38 & 0.001 & 11 & 4.55 & 0.858\\
English & 5 & 2.66 & 0.132 & 20 & 9.14 & 0.511\\
French & 8 & 2.81 & 0.133 & 20 & 3.75 & 0.112\\
Italian & 4 & 2.93 & 0.608 & 9 & 9.45 & 0.780\\
Norwegian & 5 & 2.88 & 0.201 & 15 & 6.28 & 0.744\\
Russian & 24 & 5.61 & 0.723 & 8 & 4.20 & 0.541\\
Spanish & 4 & 2.98 & 0.460 & 13 & 8.75 & 0.736\\
Swedish & 4 & 2.49 & 0.171 & 11 & 4.68 & 0.103\\
Turkish & 4 & 2.87 & 0.925 & 8 & 3.26 & 0.375\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:powerLawComp}Results of fitting a power-law model to the degree distribution in each model for comprehension data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power-law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Sem.} & \multicolumn{3}{c}{Phono.} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
\midrule
Croatian & 5 & 2.67 & 0.895 & 2 & 2.06 & 0.020\\
Danish & 4 & 2.39 & 0.005 & 5 & 2.98 & 0.136\\
English & 4 & 2.64 & 0.765 & 13 & 5.16 & 0.235\\
French & 4 & 2.63 & 0.330 & 18 & 5.58 & 0.336\\
Italian & 4 & 2.88 & 0.688 & 8 & 10.27 & 0.909\\
Norwegian & 5 & 2.87 & 0.433 & 13 & 7.65 & 0.440\\
Russian & 8 & 3.91 & 0.952 & 5 & 3.97 & 0.854\\
Spanish & 5 & 3.11 & 0.552 & 5 & 3.01 & 0.085\\
Swedish & 5 & 2.81 & 0.713 & 9 & 6.75 & 0.102\\
Turkish & 4 & 3.13 & 0.887 & 9 & 5.73 & 0.958\\
\bottomrule
\end{tabular}
\end{table}

In brief, the analysis consisted in two steps. First, we derived the optimal cut-off, \(k_{min}\), above which the distribution is more likely to follow a power-law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter \(\alpha\). Second, we calculated the goodness-to-fit, which resulted in a \(p\)-value quantifying the plausibility of the model. The results are shown in Table \ref{tab:powerLawProd} for production data, and in Table \ref{tab:powerLawComp} for comprehension data.

Overall, we could not reject the null hypothesis of a power-law distribution: The \(p\)-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. These \enquote{truncated} power-laws in phonological networks may be due to the constraints that exist on word formation in the phonological domain such as the size of the phonemic inventory, phonotactic rules, and word length. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions that decay faster than a non-truncated power law (Arbesman et al., 2010).

@@

We estimated the parameter \(\beta\) using a Bayesian approach. The inference was performed using the probabilistic programming language WebPPL (Goodman \& Stuhlmuller, 2014). We defined a uniform prior over \(\beta\), and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using Formula 1). Markov Chain Monte Carlo sampling resulted in a posterior distribution over \(\beta\), which we summarized in Figure \ref{fig:growthPred}. The results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT. Crucially, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages. This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption; rather, it supports our initial approximation about the shared nature of the semantic similarity measure. That said, this approximation is not perfect. For example, there is evidence that a small part of the variance in free association data can be explained by phonological similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson, 2018), thus leading to possibly minor cross-linguistic differences.} and phonological domains. In Appendix B, we show that the semantic and phonological domains provide largely non-redundant information.

@@

As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences. Connectivity contributes to learning in some languages but not in others. In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency, and length. This finding contrasts with the original finding in Hills et al. (2009). However, this difference might be due to our using a slightly different model (which included word length as a covariate) and a larger dataset. That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model (Figure \ref{fig:staticAll}).

@@

One possibility is that these patterns emerge from children's use of statistical learning abilities (Aslin \& Newport, 2012; Saffran, Aslin, \& Newport, 1996; Smith \& Yu, 2008). The term \enquote{statistical learning} has been used in the developmental literature to describes the process by which one acquires information about their environment through tracking the frequency distribution of some elements (e.g., words) in different contexts. An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input. Previous work in this line of research has documented specific mechanisms that can explain the patterns found in the current study.

For example, in the semantic domain, growth according to EXT could be explained by a mechanism similar to cross-situational learning (McMurray et al., 2012; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents. The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word \enquote{ball} is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings. In our case, free association (used to determine semantic network connectivity) is related to contextual co-occurrence (Fourtassi \& Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected words will tend to occur in a variety of speech and referential contexts. This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts. Crucially, children can learn these words without necessarily knowing the meaning of all other words with which they co-occur (Fourtassi, Dunbar, \& Dupoux, 2014), hence the similarity with EXT. This possibility is supported by the finding that words' diversity of occurrence in child-directed speech predicts their age of learning (Hills et al., 2010; Stella et al., 2017).

@@

This work shares a number of limitations with previous studies using similar research strategy and datasets. Chief among these limitations is the fact that the age of word acquisition is computed using different children at different ages (due to the fact that available CDI data is mainly cross-sectional). Such a measure has been shown to be valid and reliable (Fenson et al., 1994), and has allowed researchers to study important aspects of word learning (Braginsky et al., 2019; Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel, 2009). In our case, the use of cost-effective cross-sectional data has allowed us to leverage large-scale studies across several languages. That said, it is important to remember that this type of data can only inform us about the learning trajectory of the \enquote{average} child. Although our study endorses, overall, the externally-driven account of network growth, this does not mean individual children never use some variant of INT or some combination of both INT and EXT (Beckage \& Colunga, 2019). To illustrate, some children develop \enquote{islands of expertise,} that is, well-organized knowledge about a certain topic (e.g., birds or dinosaurs). This prior knowledge enables these children to learn new related words more easily (e.g., Chi \& Koeske, 1983).

@@

\hypertarget{appendix-a-analyses-using-different-phonological-distances}{%
\section{Appendix A: Analyses using different phonological distances}\label{appendix-a-analyses-using-different-phonological-distances}}

@@

We show in Figure \ref{fig:corrPlot} the correlation between the phonological connectivity and age of acquisition in both comprehension and production. The sparsity issue --- due to the low phonological neighborhood in the children's lexicon --- is apparent: Most words had 0 connectivity, and a few had non-zero but small degrees. The values of the correlations are much lower than the ones obtained with a threshold of 2.

The next figures show how the phonology-based mechanism of growth (phonoEXT) fares in comparison to semEXT and other predictors of learning in each language (Figure \ref{fig:staticPredEdit1}) and across all languages (Figure \ref{fig:staticAllEdit}). These figures show that phonoEXT based on edit distance 1 had no noticeable effect on learning.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Age of acquisition in both comprehension and production as predicted by the degree (i.e., connectivity) in the phonological networks, using an edit distance of 1. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPredEdit1-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression models. The phonological networks were based on an edit distance of 1. Ranges indicate 95\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).}\label{fig:staticPredEdit1}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model. The phonological networks were based on an edit distance of 1. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllEdit}
\end{figure}

@@

We constructed weighted phonological networks where the edge between a given pair of words \((w_1, w_2)\) was weighted by a measure of similarity defined as \(1-NED(w_1,w_2)\), where \(NED(w_1,w_2)\) is the Normalized Edit Distance with values in the range \([0,1]\). We obtain \(NED(w_1,w_2)\) by dividing the edit distance by the maximum possible distance between the two words, that is, the length of the longer word. The phonological connectivity of a given word \(w\) was defined as the sum over all weighted edges with every other word \(w_i\) in the network, i.e., \(\sum_{i} (1-NED(w,w_i))\).

The results were as follows. The correlations were lower than the ones obtained with the thresholds 2 and 1 (Figure \ref{fig:corrPlotnt}). That sais, we found a (slight) predictive effect of phonoEXT when controlling for frequency and length (Figures \ref{fig:staticPrednt} and \ref{fig:staticAllnt}).

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlotnt-1} \caption{Age of acquisition in both comprehension and production as predicted by the connectivity in the phonological network, using weighted edges. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlotnt}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPrednt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the regression models. In the phonological networks, the edges between pairs of words were weighted by a normalized edit distance. Ranges indicate 95\% confidence intervals. Positive values indicate a positive relationship (e.g., longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g., words with higher frequency tend to have a lower AoA).}\label{fig:staticPrednt}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model. In the phonological networks, the edges between pairs of words were weighted by a normalized edit distance. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllnt}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPair-1} \caption{The distribution of the Pearson correlation coefficients of the unilemma's phonological connectivity between every pair of languages.}\label{fig:corrPair}
\end{figure}

@@

\leavevmode\hypertarget{ref-beckage2019}{}%
Beckage, N. M., \& Colunga, E. (2019). Network growth modeling to capture individual lexical learning. \emph{Complexity}.

@@

\leavevmode\hypertarget{ref-fourtassi2014}{}%
Fourtassi, A., Dunbar, E., \& Dupoux, E. (2014). Self-consistency as an inductive bias in early language acquisition. In \emph{Proceedings of the annual meeting of the cognitive science society}.
